A thesis draft

### 2018-11-22 res/sections/81-k8s.tex
Fix typos

First of all the software needed must be installed and for this the script 
\\\verb!install_kubectl_repo.sh!
\footnote{\url{https://raw.githubusercontent.com/Augugrumi/init-script/centos/kubernetes/install_kubectl_repo.sh}}
was created. This only calls another script and waits until all the machines
are ready. The other script is \verb!bootstrap.sh!
\footnote{\url{https://raw.githubusercontent.com/Augugrumi/vagrantfiles/oldversion/kubernetes/centos/bootstrap.sh}}
whose aim is to configure the machine and to install all the necessary
software. The boostrap script first \textbf{disables SELinux} on all machines 
(needed for Kubernetes networking):
\begin{lstlisting}
sudo setenforce 0
sudo sed -i --follow-symlinks 's/SELINUX=enforcing/SELINUX=disabled/g' /etc/sysconfig/selinux
\end{lstlisting}

@@

The next step is to install 
Flannel\footnote{\url{https://github.com/coreos/flannel}}
in order to get the networking working. Some time is necessay until the 
networking is up:
\begin{lstlisting}
kubectl apply -f https://raw.githubusercontent.com/coreos/flannel/master/Documentation/kube-flannel.yml
kubectl apply -f https://raw.githubusercontent.com/coreos/flannel/master/Documentation/k8s-manifests/kube-flannel-rbac.yml
\end{lstlisting}

>>>>

First of all the software needed must be installed and for this the script 
\\\verb!install_kubectl_repo.sh!
\footnote{\url{https://raw.githubusercontent.com/Augugrumi/init-script/centos/kubernetes/install_kubectl_repo.sh}}
was created. This only calls another script and waits until all the machines
are ready. The other script is \verb!bootstrap.sh!
\footnote{\url{https://raw.githubusercontent.com/Augugrumi/vagrantfiles/oldversion/kubernetes/centos/bootstrap.sh}}
whose aim is to configure the machine and to install all the necessary
software. The bootstrap script first \textbf{disables SELinux} on all machines 
(needed for Kubernetes networking):
\begin{lstlisting}
sudo setenforce 0
sudo sed -i --follow-symlinks 's/SELINUX=enforcing/SELINUX=disabled/g' /etc/sysconfig/selinux
\end{lstlisting}

@@

The next step is to install 
Flannel\footnote{\url{https://github.com/coreos/flannel}}
in order to get the networking working. Some time is necessary until the 
networking is up:
\begin{lstlisting}
kubectl apply -f https://raw.githubusercontent.com/coreos/flannel/master/Documentation/kube-flannel.yml
kubectl apply -f https://raw.githubusercontent.com/coreos/flannel/master/Documentation/k8s-manifests/kube-flannel-rbac.yml
\end{lstlisting}
